Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-03 supp.rnw
Remove a completed TODO.
Make macros for the supplementary plots to prevent text duplication.

@@

	\caption{%
		Plot of model fit using the most parsimonious model.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}
	\label{fig:model-fit-best}
\end{figure}

@@

	\caption{%
		Plot of model fit using the model average model.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}
	\label{fig:model-fit-average}
\end{figure}

@@

	\caption{%
		Partial residual plots showing the effects of competition coefficients in the most parsimonious model.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}
	\label{fig:partial-residual-best}
\end{figure}

@@

	\caption{%
		Partial residual plots showing the effects of competition coefficients in model average model.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}
	\label{fig:partial-residual-average}
\end{figure}

>>>>

\newcommand\modelfitplotcaption[1]{%
	\caption{%
		Plot of model fit using the #1.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}%
}
\newcommand\partialresidualplotcaption[1]{%
	\caption{%
		Partial residual plots showing the effects of competition coefficients in the #1.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}%
}

@@

	\modelfitplotcaption{most parsimonious model}
	\label{fig:model-fit-best}
\end{figure}

@@

	\modelfitplotcaption{model average model}
	\label{fig:model-fit-average}
\end{figure}

@@

	\partialresidualplotcaption{most parsimonious model}
	\label{fig:partial-residual-best}
\end{figure}

@@

	\partialresidualplotcaption{model average model}
	\label{fig:partial-residual-average}
\end{figure}
